Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-15 paper.qmd
Stats19 tweaks

```{r}
#| label: stats19
#| include: false
years = 2021:2022
dir.create("data/stats19", recursive = TRUE, showWarnings = FALSE)
collisions_2022 = stats19::get_stats19(year = 2022)
collisions_2021 = stats19::get_stats19(year = 2021)
collisions_2020 = stats19::get_stats19(year = 2020)
collisions = bind_rows(collisions_2020, collisions_2021, collisions_2022)
# collisions_2021 = stats19::get_stats19(year = 2021)
# collisions = purrr::map_df(years, stats19::get_stats19, type = "collision", data_dir = "data/stats19")
stats19_monthly = collisions |>
  filter(police_force == "West Yorkshire") |>
  mutate(month = lubridate::floor_date(date, "month")) |>
  group_by(month) |>
  summarise(n = n()) |>
  mutate(records = "stats19")

@@

OpSnap data should be compared to, and integrated with, other road safety datasets.
For example, spatial analysis that was Integrated with Strava data (road use data by cyclists and pedestrians), Google road use and other data, may facilitate exposure-based measures rather than the counts used here.
The use of rates will enhance the identification locations with higher risk because based on their volume of traffic: different types of risk need to be gauged.
Comparison and integration of OpSnap and Stats193 is an obvious starting point.
To what extent do OpSnap and Crashmap incidents overlap?
To what extent are they complementary?
To what extent do they identify the same or different types of problems?

>>>>

```{r}
#| label: stats19
#| include: false
# years = 2021:2022
# dir.create("data/stats19", recursive = TRUE, showWarnings = FALSE)
# collisions_2022 = stats19::get_stats19(year = 2022)
# collisions_2021 = stats19::get_stats19(year = 2021)
# collisions_2020 = stats19::get_stats19(year = 2020)
# collisions = bind_rows(collisions_2020, collisions_2021, collisions_2022)
# write_csv(collisions, "collisions_2020-2022.csv")
# piggyback::pb_upload("collisions_2020-2022.csv")
system("gh release download v1")
collisions = read_csv("collisions_2020-2022.csv")
stats19_monthly = collisions |>
  filter(police_force == "West Yorkshire") |>
  mutate(month = lubridate::floor_date(date, "month")) |>
  group_by(month) |>
  summarise(n = n()) |>
  mutate(records = "stats19")

@@

OpSnap data should be compared to, and integrated with, other road safety datasets.
For example, spatial analysis that was Integrated with Strava data (road use data by cyclists and pedestrians), Google road use and other data, may facilitate exposure-based measures rather than the counts used here.
The use of rates will enhance the identification locations with higher risk because based on their volume of traffic: different types of risk need to be gauged.
Comparison and integration of OpSnap and STATS19 datasets could provide a logical starting point.
To what extent are OpSnap and STATS19 records overlapping or complementary?
To what extent do they identify the same or different types of problems?
